03 Data Vizualization

### 2022-03-29 03_data_viz.Rmd
Update 03_data_viz.Rmd

## Microbial turnover rate across soil types

@@

```{r}
p_dF <- turnover_summarized %>% 
  filter(time_course == "0d -->") %>% 
  ungroup() %>% 
  select(terrain, inc_time_d, compound, dF) %>%
  left_join(
    turnover_weighted %>% 
      select(terrain, inc_time_d, dF_weighted), 
    by = c("terrain", "inc_time_d")) %>% 
  group_by(
    terrain,
    inc_time_d
  ) %>% 
  pivot_longer(
    cols = c(dF, dF_weighted),
    values_to = "dF", 
    names_to = "type"
  ) %>% view()

@@

peaks_mapped_summarized_wppm <- peaks_mapped_summarized %>% 
    mutate(at2H_ppm = at2H * 10000,
         at2H_mn_zero_ppm = at2H_mn_zero * 10000,
         at2H_weighted_ppm = at2H_weighted * 10000)

>>>>

## Turnover distributions

@@

```{r}
p_dF <- turnover_summarized %>% 
  filter(time_course == "0d -->") %>% 
  ungroup() %>% 
  select(terrain, inc_time_d, compound, dF) %>%
  left_join(
    turnover_weighted %>% 
      select(terrain, inc_time_d, dF_weighted), 
    by = c("terrain", "inc_time_d")) %>% 
  group_by(
    terrain,
    inc_time_d
  ) %>% 
  pivot_longer(
    cols = c(dF, dF_weighted),
    values_to = "dF", 
    names_to = "type"
  ) %>%

@@

peaks_mapped_summarized_wppm <- turnover_summarized %>% 
    mutate(at2H_ppm = at2H * 10000,
         at2H_mn_zero_ppm = at2H_mn_zero * 10000,
         at2H_weighted_ppm = at2H_weighted * 10000)
